Toggle Smell Detection in Google Chrome

### 2015-12-08 paper/paper.tex
merging

\section{Introduction}
Identifying code smell is a vital task for better re-factoring. Large amount of effort could be saved if a bad smell in a software project is detected properly. Re-factoring becomes more costly when there is lack of proper development documentations. Feature oriented Model Driven Development allows us develop software system to grow up in a feature oriented way that dictates the features to be distinguishable and understandable. To develop features in an isolated way while developing on a single trunk major software companies including Google~\cite{ChromeRepidRelease}, Facebook~\cite{Rossi2014Google} and Netflix use feature toggles to enable or disable a feature from the end-user access. However, improper use of feature toggles is a bad practice~\cite{Fowler2010FeatureToggle}. Feature toggles hide feature 
related code blocks until the feature is ready to publish. Once the 
development of a feature is done and published but still the toggle is 
left in the code, the blocked code becomes a dead code which is a technical 
debt.\\

@@

\subsection{Compile-Time Macros}
TODO: Faruk

@@

\item{Avoiding ‘N’ passes
\begin{itemize}
\item At present for each smell detection type, the algorithm scans the same set of files again and again. This would lead to scaling problem when ran on a large module. We have already observed with the results indicating 41 minutes to scan the “chrome” module for each smell detection. This is significant problem with the current algorithm.
\item {
Instead a common data structure could be built by a single pass of the entire source code which could be leveraged by each smell detection algorithm. This has the following advantages
  \begin{enumerate}
  \item Overall running time for all the algorithm improves significantly.
  \item Each smell detector does not need to scan the entire source file and build the abstract syntax trees. The common data structure could be leveraged to go to particular location within the source and perform a coarse grained search.
   \item Some files where there are no toggle method invocations will be ignored by each of the smell detection algorithms. For example, currently if there are ‘N’ files which does not have any toggle method invocation, then each file is parsed and AST is generated and then it is checked further. This overhead time will be saved.
  \end{enumerate}
}
\end{itemize}
}

\item{Automatic detection of dead/stable toggles
\begin{itemize}
\item Our approach currently expects list of dead/stable toggles to be provided as an input by the user. But this could be avoided if alternate MSR techniques are implemented to detect the code chunks which involves changing the state of the toggle flags in test and live environment and derive the list of stable/dead toggles in an automated way. However we don’t have any approach in thought as of now.
\end{itemize}
}
\end{enumerate}

\section{Threats to validity}
\label{Threats to validity}

Though we have done extensive study on google chromium project and came up with classification of code smells, we haven’t done exploratory study on other projects to confirm the presence of toggle smells we defined in this research. There are several reasons for this

\begin{enumerate}
\item{Not many open source projects are using feature toggles.
\begin{enumerate}
\item In our search we found only one more project in the github location named “go.cd” which has feature toggle implementation. But the project was using JRuby and Java as the primary languages.
\end{enumerate}
}
\item {No evolution history of toggle usage
\begin{enumerate}
\item Google chrome project has been using feature toggles for more than 5 years and has an evolution history to mine the source code repository. We are yet to find another project which has the evolution and data to mine.
\end{enumerate}
}

>>>>

\section{Introduction}
Identifying code smell is a vital task for better re-factoring. Large amount of effort could be saved if a bad smell in a software project is detected properly. Re-factoring becomes more costly when there is lack of proper development documentations. Feature oriented Model Driven Development allows us develop software system to grow up in a feature oriented way that dictates the features to be distinguishable and understandable. To develop features in an isolated way while developing on a single trunk major software companies including Google~\cite{ChromeRepidRelease}, Facebook~\cite{Rossi2014Google} and Netflix~\cite{NetFlixCasandra} use feature toggles to enable or disable a feature from the end-user access. However, improper use of feature toggles is a bad practice~\cite{Fowler2010FeatureToggle}. Feature toggles hide feature 
related code blocks until the feature is ready to publish. Once the 
development of a feature is done and published but still the toggle is 
left in the code, the blocked code becomes a dead code which is a technical 
debt.\\

@@

\subsection{Compile-Time Macros}
This kind of usage is predominant in languages which support macros (C, C++) and used for conditional compilation. This violates the fundamental principle of the feature toggles. Even though feature toggle experts does not recommend this approach, some still prefer to use.
\begin{lstlisting}
#ifdef FEATURE1
….
#endif
\end{lstlisting}

\subsection{Run time toggles}
Run time toggles usage comes in two flavors, in one the state of the feature flags will be modified without restarting the program or service managing the feature, in another flavor the toggle value will be changed, but requires restart of the program or service. The deployment model depends on the infrastructure of the target environment. The advantage of the run time toggle when compared to the compile time toggles is that they don’t require touching the source code file and regenerate the binary. In languages similar to Javascript, where binary generation is not required because of the execution model, keeping the toggle repository separate from the source code (in the form of JSON) will prevent the minification process.

There are different ways to doing this:

\subsubsection{Live Update With Program Restart}

\begin{itemize}
\item External files (.json, .properties, .csv) with one time loading
\item Command Line Arguments
\end{itemize}

\subsubsection{Live update without program restart}
\begin{itemize}
\item External files with auto reloading
\item Private API or Interface to change toggle state
\end{itemize}

@@

\item{Avoiding ‘N’ passes
\begin{itemize}
\item At present for each smell detection type, the algorithm scans the same set of files again and again. This would lead to scaling problem when ran on a large module. We have already observed with the results indicating 41 minutes to scan the “chrome” module for each smell detection. This is significant problem with the current algorithm.
\item Instead a common data structure could be built by a single pass of the entire source code which could be leveraged by each smell detection algorithm. This has the following advantages
\end{itemize}
}

\item{User interface
\begin{itemize}
\item 
\item
\end{itemize}
}
